---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rphl

<!-- badges: start -->
<!-- badges: end -->

The `rphl` package contains R code for quickly creating figures using the City of Philadelphia's [visual standards](https://standards.phila.gov/guidelines/design-development/brand-elements/), including the color palette and typography.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("CityOfPhiladelphia/rphl")
```

In order to use the package, you will have to install [Open Sans](https://fonts.google.com/specimen/Open+Sans) and [Montserrat](https://fonts.google.com/specimen/Montserrat) on your computer, and use the `extrafont` package to load the fonts into R:

``` r
# extrafont should install with rphl. If not, install from CRAN:
# install.packages("extrafont")
extrafont::font_import()
```

## Example

```{r example}
library(rphl)
library(ggplot2)
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 3) +
  scale_color_phl() +
  theme_phl()
```

